---
title: "Denver 1 Bedroom Condos 80202"
author: "Matt Majestic"
date: "Feb 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(flexdashboard)
library(Quandl)
library(ggplot2)
library(plotly)
library(dplyr)
library(lubridate)
library(tidyr)
library(DT)
library(dygraphs)

Quandl.api_key('JJLzxHGAE8n9mFR1pLbb')

Zillow_Listing_Median <- Quandl('ZILLOW/Z80202_MLP1B')
Zillow_ValueIndex <- Quandl('ZILLOW/Z80202_ZHVI1B')
Zillow_HVI_PriceCut_Median <- Quandl('ZILLOW/Z80202_MPCDCO')

listing_pivot <- Zillow_Listing_Median %>% filter(Date > "2018-12-31") %>% mutate(Year = year(Date),Month = month(Date)) 
annual_growth <- listing_pivot %>% filter(Month == 1 | Month == 12) 
annual_growth_percent <- data.frame("Annual Growth Percentage" = ((annual_growth[1,"Value"] -annual_growth[2,"Value"]) / annual_growth[1,"Value"]))
Listing_lp <- ggplotly(ggplot(Zillow_Listing_Median,aes(Date,Value)) + geom_line() + geom_point() + labs(title = 'Zillow Median Listing Prices'))
HVI_lp <- ggplotly(ggplot(Zillow_ValueIndex,aes(Date,Value)) + geom_line() + geom_point() + labs(title = 'Zillow HVI from Purchase Date to Present'))
HVI_Pricecut_lp <- ggplotly(ggplot(Zillow_HVI_PriceCut_Median,aes(Date,Value)) + geom_line() + geom_point() + labs(title = 'Zillow HVI Median Price Cut for Condos 80202'))

```
## Synopsis 

Based on this evaluation, Unit 1001 of 444 17th St Denver, CO 80202 is worth **$275,000** as the housing market data from **Zillow** suggests flat/slightly negative metrics of the growth for 1 bedroom units in 80202.  This property was bought for **$269,000** slightly over a year ago.  Therefore an offer of **$275,000** is a reasonable price for both parties as the seller nets **$6,000** in slightly over a year **without conducting any major renovations** especially given the **flat trends from the Zillow Housing Data** below.    


## Median Listing Price

The median price since the unit has been purchased has decreased by **-1 %**


```{r list_lp,echo =FALSE}
Listing_lp
```

### The median listing prices from purchase to end of 2019 (YoY)
```{r dt,echo =FALSE}
datatable(annual_growth %>% select(Date,Value),rownames = FALSE,options = list(searching = FALSE)) %>% formatCurrency("Value",digits = 0)
```

### Growth since Purchase
```{r percent,echo =FALSE}
datatable(annual_growth_percent,rownames = FALSE,options = list(searching = FALSE)) %>% formatPercentage("Annual.Growth.Percentage",digits = 3)
```

## The **Zillow Home Value Index** since the unit has been bought in 2019

#### Zillow HVI is flat/slightly negative since 2019

```{r hvi, echo=FALSE}
HVI_lp
```

## The **Zillow Home Value Index** suggests the median price cut be **at least $10K**

#### The suggested offer of **$275,000** coincides with the proposed logic

```{r hvi_pc, echo=FALSE}
HVI_Pricecut_lp
```

## Conclusion

#### The data provided by Zillow reflects the market for 444 17th Street Denver, CO 80202 being flat which makes the unit of 1001 worth **$275,000** as **no major renovations had been conducted** in the year of ownership.

Note all this data is from Zillow's API via Quandl
